---
title: "Final_project"
output: html_document
---
# Loading packages

```{r}
library(tidyverse)
```
# Loading data


```{r}
life_exp <- read_csv("Data/life-expectancy.csv")

health_expend <- read.csv("Data/public-expenditure-on-healthcare-as-share-of-national-gdp.csv")

pop_change <- read.csv("Data/population.csv")

```


# Removing space in columnname in data on life expectancy
```{r}
life_exp %>% 
  rename(Life_expectancy = `Life expectancy`) -> life_exp
```


# Visualising graphs on life expectancy in the US, Japan and Norway


```{r}
life_exp %>% 
  filter(Entity %in% c("United States", "Japan", "Norway")) %>% 
  ggplot()+
  geom_line(mapping = aes(x = Year, y = Life_expectancy))+
  facet_wrap(~Entity, ncol = 2)
```


# Renaming last column in the data on health expenditure

```{r}
health_expend %>% 
  rename(Public_health_expenditure = `Public.Expenditure.on.Health..Tanzi...Schuktnecht..2000..`) -> health_expend
```

# Visualising data on annual health expenditure for the chosen countries

```{r}
health_expend %>% 
  filter(Entity %in% c("United States", "Japan", "Norway")) %>% 
  ggplot()+
  geom_line(mapping = aes(x = Year, y = Public_health_expenditure))+
  facet_wrap(~Entity, ncol = 2)
```

# Renaming last column in data on population change

```{r}
pop_change %>% 
  rename(Population_change = `Total.population..Gapminder..HYDE...UN.`) -> pop_change
```

# Visualising data on population change in the chosen countries

```{r}
pop_change %>% 
  filter(Entity %in% c("United States", "Japan", "Norway")) %>% 
  ggplot()+
  geom_line(mapping = aes(x = Year, y = Population_change))+
  facet_wrap(~Entity, ncol = 2)

options(scipen = 999)
```

